---
title: "ForLiveAssignment12_RiccoFerraro"
author: "Ricco Ferraro"
date: "3/23/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r }
library(shiny)

ui <- fluidPage(
  # App title ----
  tabsetPanel(
    tabPanel("About Me:", h3("Ricco Ferraro"), div("Senior Software Engineer, Tandem Diabetes Care"), div("Masters of Data Science student at SMU"), div("San Luis Obispo, CA"), imageOutput("profilePic"), div("“The other tabs represent work / analyses that I have completed.  Please check them out!”")),
    tabPanel("Beer Study", includeHTML("BeersAndBrews.html")),
    tabPanel("TODO", div("fill this in"))
  ),
  # # Sidebar layout with input and output definitions ----
  # sidebarLayout(
  # 
  #   # Sidebar panel for inputs ----
  #   sidebarPanel(
  # 
  #     # Input: Slider for the number of bins ----
  #     sliderInput(inputId = "bins",
  #                 label = "Number of bins:",
  #                 min = 1,
  #                 max = 50,
  #                 value = 30)
  #   ),
  #   # Main panel for displaying outputs ----
  #   mainPanel(
  #     # Output: Histogram ----
  #     plotOutput(outputId = "distPlot")
  #   )
  # )
)


# Define server logic required to draw a histogram ----
server <- function(input, output) {
  
  # Histogram of the Old Faithful Geyser Data ----
  # with requested number of bins
  # This expression that generates a histogram is wrapped in a call
  # to renderPlot to indicate that:
  #
  # 1. It is "reactive" and therefore should be automatically
  #    re-executed when inputs (input$bins) change
  # # 2. Its output type is a plot
  # output$distPlot <- renderPlot({0
  #   
  #   x    <- faithful$waiting
  #   bins <- seq(min(x), max(x), length.out = input$bins + 1)
  #   
  #   hist(x, breaks = bins, col = "#75AADB", border = "white",
  #        xlab = "Waiting time to next eruption (in mins)",
  #        main = "Histogram of waiting times")
  #   
  # })
  output$profilePic <- renderImage({
    list(src = "./profilePic.png",
         # height = 400, 
         # width = 300,
         alt = paste("ProfilePic", input$n))
  })
}


shinyApp(ui, server)

```


Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



